---
title: "Chin_W9"
author: "Madison Chin"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,root.dir = '~/GitHub/ADV-Topics-2---DSR-w-R/WeeklyAssignments/Assignment 9') #needed to set(root.dir = '~/GitHub/ADV-Topics-2---DSR-w-R/WeeklyAssignments/Assignment 9')
library(tidyverse)
library(ggplot2)
#setwd("~/GitHub/ADV-Topics-2---DSR-w-R/WeeklyAssignments/Assignment 9")
prob_task <- read_csv("data/MFIndD_probtask.csv")
```


```{r dataprep, include = FALSE}
prob_data_mod <- prob_task%>%
  # a. Separate `left_stim` and `right_stim` based on `_` separator
  separate(left_stim, into = c("left_numerator", "left_other"), sep = "_", fill = "right") %>%
  separate(right_stim, into = c("right_numerator", "right_other"), sep = "_", fill = "right") %>%
  
  # Convert columns to numeric
  mutate(
    left_numerator = as.numeric(left_numerator),
    left_other = as.numeric(left_other),
    right_numerator = as.numeric(right_numerator),
    right_other = as.numeric(right_other)
    
  ) %>%
  
  # c. Create `left_proportion_value` and `right_proportion_value`
  mutate(
    left_proportion_value = left_numerator / (left_numerator + left_other),
    right_proportion_value = right_numerator / (right_numerator + right_other),
  # d. Create `larger_numerator`
    larger_numerator = if_else(left_numerator > right_numerator, "left", "right"),
  # e. Create `larger_proportion`
    larger_proportion = if_else(left_proportion_value > right_proportion_value, "left", "right"),
  # f. Create `num_congruent`
    num_congruent = larger_numerator == larger_proportion
  )
```

```{r doublecheckmod, include = FALSE}
head (prob_data_mod)
```

```{r dataprep2,include = FALSE}
# Summarize data for plotting
plot_mod <- prob_data_mod %>%
  group_by(SubID,condition, num_congruent) %>%
  summarize(proportion_correct = mean(correct), .groups = 'drop')
#stat_halfeye still not working even though ggplot is in setup chunk
library(ggdist)
# Create the plot using `stat_halfeye`
ggplot(plot_mod, aes(x = condition, y = proportion_correct, color = num_congruent)) +
  stat_halfeye() +
  labs(
    x = "Condition",
    y = "Proportion Correct",
    color = "Numerator Congruency"
  ) +
  theme_minimal() +
  theme(legend.position = "top")

print(plot_mod)

```

```{r doublecheckplotmod, include = FALSE}
plot_mod
```

## Slide 1: Big Research Question

**How do people think proportionally with different kinds of stimuli?**

## Slide 2: Little Research Question (Fork)

In this analysis, we’re asking a specific question: **"How does the congruence of numerators and proportions affect participants' accuracy in selecting the larger proportion?"**

We are examining: - Whether the *larger numerator* corresponds with the *larger proportion* across different conditions. - How participants perform under conditions of congruency (when the larger numerator aligns with the larger proportion) vs. incongruency.

## Slide 3: Plot of Proportion Correct by Condition and Congruency

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Summarize data for plotting
plot_mod <- prob_data_mod %>%
  group_by(SubID,condition, num_congruent) %>%
  summarize(proportion_correct = mean(correct), .groups = 'drop')
#stat_halfeye still not working even though ggplot is in setup chunk
library(ggdist)
# Create the plot using `stat_halfeye`
ggplot(plot_mod, aes(x = condition, y = proportion_correct, color = num_congruent)) +
  stat_halfeye() +
  labs(
    x = "Condition",
    y = "Proportion Correct",
    color = "Numerator Congruency"
  ) +
  theme_minimal() +
  theme(legend.position = "top")

```
