---
title: "How Does PTSD Hypervigilance Impact Event Segmentation?"
author: "Madison Chin"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(readxl)
library(ggthemes)
knitr::opts_chunk$set(echo = FALSE,root.dir = '~/GitHub/ADV-Topics-2---DSR-w-R/Final Project Materials')

```


## Research Questions

### Big Question:
How does PTSD influence the way individuals perceive and segment everyday activities into meaningful events?

### Little Question:
How do individual PTSD participants' mean segmentation agreement scores vary across a movie, and what patterns of clustering or dispersion emerge in their performance?


## Data Source :{.smaller}
### Sources:
- **Study**: 
- Post-traumatic Stress and the Comprehension of 
  Everyday Activity by Michelle L. Eisenberg, Jesse Q. Sargent, and Jeffrey M. Zacks.
  
- **Participants**: 
- 137 individuals, aged 21–79, with varying PTSD symptom severity.
- 51% female; 72% White; mean age = 50 years. 
- Participants were recruited immediately after their participation in a cross-sectional study of the relationship between age, cognitive ability, and event segmentation.

## Tasks/Methods:{.smaller}
- Reciting recollection of events after viewing them in a movie (for 3 Movies).
- PTSD severity was measured using the Traumatic Life Events Questionnaire(TLEQ).
- Button-press segmentation of coarse and fine-grained events(pressing when the beginning and end of "large" or "small" events occur) while viewing visual stimuli(3 Movies).
  - Each participant's segmentation (coarse and fine) was compared to the group's overall segmentation using correlations.
  - These correlations were scaled to a 0–1 range, with 1 representing maximum agreement and 0 representing no agreement. 
  - Finally, the coarse and fine segmentation scores were averaged to get a final segmentation agreement score for each participant.



```{r justthetable, echo = TRUE, include = FALSE }
#viewing to make sure that all info from chosen dataset is being processed correctly.
data3 <- readxl::read_excel("MaterialData/SegmentationAgreement-scored-corr.xlsx",sheet = 2 )
head(data3)
```

## Segmentation Agreement for First Movie: Coarse and Fine Events

```{r fixing_na_data, include = FALSE}
# Remove rows where all relevant columns are NA
#These represent participants that left/were unable to complete the scoring assignment.
clean_data <- data3 %>%
  filter(rowSums(is.na(select(., AgrMov1:AgrMov3))) != ncol(select(., AgrMov1:AgrMov3)))

tail(clean_data) #checking to make sure that the tailing participants who have null data are erased.

```

```{r plot, include = TRUE, fig.width=8, fig.height= 4}
# Create a box plot for AgrMov1 (Segmentation Agreement Scores(For coarse and fine grained events (avged out by experimenters)) for First Movie shown to participants)
ptsd_boxplot <- ggplot(clean_data, aes(x = participant_id, y = AgrMov1)) +
  geom_point(color = "darkblue") +
  labs(
    title = "Movie 1 Segmentation Scores among participants",
    y = "Segmentation Agreement Scores",
    x = "Participant ID's",
    caption = "Figure: Distribution of Segmentation Agreement scores for the First Movie viewing for participants."
  ) +
  theme_clean() + 
  theme(plot.caption = element_text(hjust = 0.5)) +
  ylim(0,1) + 
  geom_hline(yintercept = 0.5, color = "red") #Here is what the "norm" of segmenters should lie, according to experimenters.

# Print the plot
print(ptsd_boxplot)
```


