---
title: "Data Exercise 1 : Decision Making "
author: "Madison Chin"
date: "`r Sys.Date()`"
output: html_notebook
---


#Data Exercise 1
```{r}
library(tidyverse)
```


```{r}
de1 <- read_csv("CogSci412_DE1_data.csv") %>%
  filter(Progress == 100 & Status == "IP Address") %>%
  mutate(condition = case_when(is.na( FL_39_DO) == FALSE ~ FL_39_DO, # if this condition is true do this first case
                               is.na( FL_43_DO) == FALSE ~ FL_43_DO,))%>% #if not do this second case
  #selecting and renaming variables that we want into a cleaner dataset.

  select(ResponseId,
         condition,
         familiarity = Q10,
         pencil_control = `Pencil Control`, 
         pencil_control_conf = `Conf. Pencil Control`, 
         mag_stand = `Magazine Standard`,
         mag_stand_conf = `Conf. Mag. Stand.`, 
         mag_control = Magazine_Control,
         mag_control_conf = `Conf. Mag. Control` ,
         pencil_stnd = `Pencil_Standard`,
         pencil_stnd_conf = `Conf. Pencil Stand.`, 
         FL_42_DO,
         FL_39_DO,
         FL_43_DO)%>%
  filter(ResponseId != "BL_3ymTJ3ZOZWWbWGa|MagazineControl")
  
  

#this is the correct assignment way I think.
#na.rm removes "NA's"

```

```{r}
de1%>%
  distinct(mag_stand)
```

Is currently in wide form, we want it in long form for tidyverse

- What we want in long form 
ResponseId : unique identifier for that dataset.
Content : was the question about pencils or mags?
Type: Was the question a control question or a standard question?
Value : the actual observed number/response. 

```{r}
distinct(mag_stand)
```


```{r}
de1_longer <- de1%>%
  pivot_longer(pencil_control,pencil_stnd, #which columns to pivot
               names_to = "old_col", #where to put the old column names 
               values_to = "old_val")#where to put the data observations 
```

```{r}
 de1_longer %>%
  filter(is.na(value) == FALSE)%>%
  separate(into = c("content", "type", "DV"), col = old_col)
#is.na == TRUE when the thing is NA and is == False when the thing is not NA 
```

```{r}
de1_longer %>%
  filter(is.na(value) == FALSE)%>%
  separate(into = c("content", "type", "DV"), col = old_col)%>%
  mutate( DV = case_when(is.na (DV)==TRUE ~ "resp"
                         , DV =="conf" ~ "conf")) #sis will get prev DV replaced)
```

We have to re-code the numbers because free type seemed to mess us up a little bit.
Im just going to take notes from here on out : 
we can use parse_number() to help us organize and formulate numbers in the "correct" manner.

replace value with the number only stuff - getting rid of "cents" 
using mutate (value = parse_number (value))%>% ....
basically we hard coded her using case_when(value is less than 1 then mult by 100)

in order to analyze the stuff in the dataset, : we can do mutate to show what the correct answer is
accuracy =  if_else(value == correct answer, 
TRUE, #they're correct
FALSE #they are incorrect)

case_when seems to work better for her, recall case uses tilde for TRUE/FALSE assignments
stat = "identity" gives me the actual value inside of geom_bar
