---
title: "D2SC: Weekly Assignments"
author: "Madison Chin"
date: "`r Sys.Date()`"
output: html_notebook
---

# Initial Loading 
```{r}
#in order to load the tidyverse library you must run the following

library("tidyverse")
```

# Weekly Assignment 1

*In order to figure out which function loaded the tidyverse library, I searched the following into the Google Search Engine "load code chunk that loads tidyverse library". 

*I read the description given to me by first link "https://stackoverflow.com/questions/58289197/how-to-write-an-r-chunk-to-load-the-tidyverse"
, which after reading for a little bit, I found that someone had used the "library" function in order to load the library. 

*Then, I ran the above code chunk to figure out if the function would work for tidyverse. 

*The core tidyverse packages were correctly added, but there seems to be some "Conflicts" in the Terminal after I ran it. 

*But, after further research I found that these are not going to negatively affect any other code that I would write, but RStudio recommends using a "conflicted package" to turn these conflicts into errors.

```{r}
?tidyverse
#Below is the provided description after running #?tidyverse
```
The 'tidyverse' is a set of packages that work in harmony because they share common data representations and 'API' design. This package is designed to make it easy to install and load multiple 'tidyverse' packages in a single step. Learn more about the 'tidyverse' at https://www.tidyverse.org.

# Weekly Assignment 2

```{r}

read_csv("MFIndD_analogy.csv") #renamed 
#Here I am reading in the info from MFIndD_analogy.csv

file.rename("MFIndD_analogy.csv","Analogy_Dataset.csv")
#I was unable to find a direct function equivalent to
#the file.rename() function in  the tidyverse library

#When run, file.rename(...) returns true


```

The column that contains the unique identifier for each participate is titled "qualtrics_id" in the csv.

```{r}
analogy_data <- read_csv("Analogy_Dataset.csv")
#turning analogy data set into a usable and digestible variable. 
```


```{r}

glimpse(analogy_data)

```

2a. The above line of code results in a short "glimpse" revealing that the data set has 792 rows and 6 columns, in the first couple of lines of the output, as seen in the console when run.

```{r}
analogy_data%>%
group_by(qualtrics_id)%>%
summarise(N=n()) %>%
  distinct() %>%
  count() %>%
  head(n = 1)

  
```

2b. The above function proves that there are [99] distinct people in the trial. I could not just apply a simple summary of the amount of qualtrics_id's because there seemed to be some duplicates. This would mean that each ID is one person, so the number of unique id's would be equivalent to the total number of people in the entire experiment. 

```{r}
analogy_data%>%
group_by(qualtrics_id,trial_number)%>%
summarise(trial_number, count = n(), .groups = "drop_last")%>%
  count()
#I added the drop_last because I was getting an error"Adding missing grouping variables". 
#I have checked Stack Overflow for answers, and this one seems to work!
```



2c.Yes, everyone has data from the same number of trials. Each unique Id has  completed n trials, which for all are equal to [8] throughout the entire set. There are 99 rows which represents the number of people. So each person has data for 8 trials.