---
title: "D2SC: Weekly Assignments"
author: "Madison Chin"
date: "`r Sys.Date()`"
output: html_notebook
---

# Initial Loading 
```{r}
#in order to load the tidyverse library you must run the following

library("tidyverse")
```

# Weekly Assignment 1

*In order to figure out which function loaded the tidyverse library, I searched the following into the Google Search Engine "load code chunk that loads tidyverse library". 

*I read the description given to me by first link "https://stackoverflow.com/questions/58289197/how-to-write-an-r-chunk-to-load-the-tidyverse"
, which after reading for a little bit, I found that someone had used the "library" function in order to load the library. 

*Then, I ran the above code chunk to figure out if the function would work for tidyverse. 

*The core tidyverse packages were correctly added, but there seems to be some "Conflicts" in the Terminal after I ran it. 

*But, after further research I found that these are not going to negatively affect any other code that I would write, but RStudio recommends using a "conflicted package" to turn these conflicts into errors.

```{r}
?tidyverse
#Below is the provided description after running #?tidyverse
```
The 'tidyverse' is a set of packages that work in harmony because they share common data representations and 'API' design. This package is designed to make it easy to install and load multiple 'tidyverse' packages in a single step. Learn more about the 'tidyverse' at https://www.tidyverse.org.

# Week Assignment 2

```{r}
#setwd("C:/Users/mchin/OneDrive/Documents/GitHub/ADV-Topics-2---DSR-w-R/WeeklyAssignments/tidy_data")
#here I am checking that I have switched to the correct directory

#getwd()

# *Above,  I am grabbing the dataset from my tidydata folder (changing the directory), where MFInd resides


read_csv("MFIndD_analogy.csv") #renamed already


#Here I am reading in the info from MFIndD_analogy.csv

file.rename("MFIndD_analogy.csv","Analogy_Dataset.csv")
#When run, file.rename(...) returns true

```
The column that contains the unique identifier for each participate is titled "qualtrics_id" in the csv.

